sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2018-07-31 inst/documents/rotations_notes.Rmd
allow insecticides to continue to be used in a rotation if there are no other options remaining

@@

~ and run_id to outputs in sensi_an_rotations to make things easier in future, e.g. to identify runs with particular behaviour.

>>>>

~ added id to outputs in sensi_an_rotations to make things easier in future, e.g. to identify runs with particular behaviour.

~ also made more efficient by declaring size of results df at start of loop

The scenarios with the biggest differences seem to be where insecticide1 is the better one.
Just want to check it isn't something else screwy ???

*31/7/18*
Getting this error pushing to github :
0 [main] us 0 init_cheap: VirtualAlloc pointer is null, Win32 error 487
AllocationBase 0x0, BaseAddress 0x68570000, RegionSize 0x340000, State 0x10000
C:\Program Files (x86)\Git\bin\ssh.exe: *** Couldn't reserve space for cygwin's heap, Win32 error 0
fatal: Could not read from remote repository.

Please make sure you have the correct access rightsand the repository exists.

updating RStudio didn't fix, had once before and rebooting fixed it then ...

rebooting didn't fix, this post suggested updating git to v2 from https://gitforwindows.org/
https://stackoverflow.com/a/31970708/1718356

git --version 
git version 1.9.5.msysgit.0

now I have 2.18.0.windows1, the installer sorted uninstalling the old version, and I didn't have to change anything in RStudio.

@@

~ try a solution to the diff insecticide problem. If no other insecticides are below resistance thresh and this one is then can keep using it in a rotation ...

### 2018-07-31 inst/documents/sensi_an_rotations1.Rmd
allow insecticides to continue to be used in a rotation if there are no other options remaining

scenarios_to_plot <- c(13)

@@

  #TESTING changing min_rwr_interval from 5
  linputs$min_rwr_interval <- 0

>>>>

scenarios_to_plot <- c(21,23,32) #big difference ones all have insecticide1 as the good one
scenarios_to_plot <- c(29,38,46)
scenarios_to_plot <- c(13)

@@

  #TESTING changing min_rwr_interval from 5
  #if min_rwr_interval is set to 0 you get frequent switch backs to other insecticides 
  #for 1 generation
  #but when it's set to 5it pushes frequences above the resistance freq threshold
  linputs$min_rwr_interval <- 5
  #min_gens_switch_back has to be 0 to allow one insecticide to continue when all others dead
  linputs$min_gens_switch_back = 0
